Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-30 Ch1_movement_rates/Ch1_Figures.Rmd
Fixed captions.

```
**Figure 2** - Fitted distributions to movement rate data from estimated from radiotracking. A) lognormal distribution fitted to the twelve data points of movement rate. B) Lognormal distributions used to describe movement rates for each social group. We used the movement rate of each family group, shown by the colored dots across the x axis, as the meanlog parameter in each lognormal distribution. Due to data constraints, we used the estimated sdlog parameter from panel A to generate movement rate curves from panel B. C) movement rates used for each of the pooling scenarios. In the case of complete pooling (cp), estimated parameters from the lognormal distribution in panel A were used to calculate the expected value and this was used as the movement rate for cp. In the case of no pooling (np) we randomly sampled 30 movement rates from the distribution fitted in panel A. In the case of partial pooling (pp), we randomly sampled 6 movement rates from each social group’s curve and used these for the partial pooling simulations.

@@

grt_data %>% 
  ggplot() +
  #geom_histogram(aes(x = grt, y = ..density..), fill = my.cols1[7], bins = 20) +
  stat_function(fun = dgamma, args = list(shape = grt_fit$estimate[1], rate = grt_fit$estimate[2])) +
  #stat_function(fun = dgamma, args = list(shape = 4, scale = 5), color = "red") + 
  geom_point(aes(x = grt, color = Bird_ID, y = 0), size = 4) +
  scale_color_manual(values = c(my.cols1[4], my.cols1[2], my.cols1[3], my.cols1[1])) +
  theme_bw() +
  labs(x = "Gut retention time in minutes", y = "Density") +
  theme(legend.position = "none")+
  NULL

@@

```
**Figure 3** - Description of gut retention times using field data for four individuals, shown by each dot along the x axis. The density curve fitted corresponds to a gamma distribution with parameters shape = 2.0562 and scale = 13. 8688. This gamma distribution is later used to sample gut retention times for simulations.

@@

cbind(c("Distance", "CP", "PP", "NP"), rbind(dist_range,
                                             pextRemes(evd.fit.cp, dist_range, lower.tail = FALSE),
                                             pextRemes(evd.fit.pp, dist_range, lower.tail = FALSE),
                                             pextRemes(evd.fit.np, dist_range, lower.tail = FALSE)))

>>>>

**Figure 2** - Fitted distributions to movement rate data from estimated from radiotracking. A) lognormal distribution fitted to the twelve data points of movement rate. B) Lognormal distributions used to describe movement rates for each social group. We used the movement rate of each family group, shown by the colored dots across the x axis, as the meanlog parameter in each lognormal distribution. Due to data constraints, we used the estimated sdlog parameter from panel A to generate movement rate curves from panel B. C) movement rates used for each of the pooling scenarios. In the case of complete pooling (cp), estimated parameters from the lognormal distribution in panel A were used to calculate the expected value and this was used as the movement rate for cp. In the case of no pooling (np) we randomly sampled 30 movement rates from the distribution fitted in panel A. In the case of partial pooling (pp), we randomly sampled 6 movement rates from each social group’s curve and used these for the partial pooling simulations.

@@

grt_data %>% 
  ggplot() +
  #geom_histogram(aes(x = grt, y = ..density..), fill = my.cols1[7], bins = 20) +
  stat_function(fun = dgamma, args = list(shape = grt_fit$estimate[1], rate = grt_fit$estimate[2])) +
  #stat_function(fun = dgamma, args = list(shape = 4, scale = 5), color = "red") + 
  geom_point(aes(x = grt, color = Bird_ID, y = 0), size = 4) +
  scale_color_manual(values = c(my.cols1[4], my.cols1[2], my.cols1[3], my.cols1[1])) +
  lims(x = c(-.01, 105)) +
  theme_bw() +
  labs(x = "Gut retention time in minutes", y = "Density") +
  theme(legend.position = "none")+
  NULL

@@

**Figure 3** - Description of gut retention times using field data for four individuals, shown by each dot along the x axis. The density curve fitted corresponds to a gamma distribution with parameters shape = 2.0562 and scale = 13. 8688. This gamma distribution is later used to sample gut retention times for simulations.

@@

cbind(c("Distance", "CP", "PP", "NP"), rbind(dist_range,
                                             signif(pextRemes(evd.fit.cp, dist_range, lower.tail = FALSE), 5),
                                             signif(pextRemes(evd.fit.pp, dist_range, lower.tail = FALSE), 5),
                                             signif(pextRemes(evd.fit.np, dist_range, lower.tail = FALSE), 5)))
